---
output:
  md_document:
    variant: markdown_github
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, echo = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# yelp

This R package provides access to the [Yelp API, version 3](https://www.yelp.com/developers/documentation/v3).

## Installation and setup

To use this package, you must install it and get an access token for the API.

### Package installation

To install the package, you first need *devtool* installed.

```{r, eval = FALSE}
install.packages("devtools")
```

```{r, eval = FALSE}
devtools::install_github("richierocks/yelp")
```

### Getting the client ID and client secret

To gain access to the API, you have to [register with Yelp](https://www.yelp.com/signup), log in, and [create your own app](https://www.yelp.com/developers/v3/manage_app). This takes 5 to 10 minutes of pointing and clicking. It's reasonably self-explanatory, and there are more details on the [API Authentication](https://www.yelp.com/developers/documentation/v3/authentication) page.

Once you have registered, make a note of your *client ID* and *client secret*.

### Getting and storing an access token

You use the client ID and client secret to get an access token.

```{r, get_access_token, eval = FALSE}
access_token <- get_access_token(client_id, client_secret)
```

This access token can be passed into individual calls to the API, or you can store it so the package will automatically find it. `store_access_token(access_token)` will store it for the R session, or you can use your operating system tools to set a `YELP.ACCESS_TOKEN` environment variable to store it permanently.

## Usage

To search for businesses close to a specific location, call `business_search()` with a string giving a search term and either a string describing a location or numbers giving latitude and longitude.

```{r, business_search}
library(yelp)
business_search("pet beautician", "los angeles")
```


